Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-06-22 main.Rmd
Table 1: minute-of-day (C_2 not C_j)

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\toprule
Circular granularity & Expression & Period \\
\midrule
minute-of-hour                               &
  $C_1 = z \mod 60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_j = z \mod 60*24$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor\mod 24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor\mod 24*7$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor \mod 7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping.}
\label{tab:definitions}
\end{table}

>>>>

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\toprule
Circular granularity & Expression & Period \\
\midrule
minute-of-hour                               &
  $C_1 = z \mod 60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_2 = z \mod 60*24$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor\mod 24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor\mod 24*7$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor \mod 7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping.}
\label{tab:definitions}
\end{table}
